Zohmg---a large scale data store for aggregated time-series-based data. [DRAFT]

### 2009-05-08 doc/report/msc-report.tex
wrapped two lines - no content change.
doc/report/msc-report.tex: * cosmetic changes.

It is suitable to store the data across many storage nodes in what is called a
distributed filesystem and to to exploit the parallel nature of the records by
breaking up the data sets in pieces and have each piece be processed
separately on a node in a large compute cluster.

% TODO: fixa cites. Luckily, this is a problem that has already been solved.
Google has published papers on the MapReduce framework \cite{mapreduce}, which
allows for parallel processing of large data sets, and The Google Filesystem
\cite{gfs}, a scalable, distributed filesystem. The Apache Hadoop project has
published open source implementations of a mapreduce framework and a
distributed filesystem, both of which build on the ideas in the papers
published by Google.

@@

How to use the Zohmg system is presented in chapter 5, while chapter 6
shows an example work flow.

@@

 yield parsed.timestamp, dimensions, measurements
\end{verbatim}

@@

The last line \textit{yields} the tuple. This is a Python construct called a
generator that lets the map function emit any number of tuples (or none!)
for a single invocation.

@@

The user writes a mapper which Zohmg wraps, interpreting the output from
the mapper program and storing it in HBase.

@@

Based on the query---which the user submits---the corresponding data is
served from HBase as JSONP. The query is a simple definition of wanted row
range, dimensions, and values for these dimensions. The query is submitted
to the data server via HTTP, an example query could look like (the URL is
wrapped to fit the page) \\

\texttt{http://localhost:8086/data/?t0=20090101 \\
\&t1=20090420\&unit=pageviews\&d0=country\&d0v=SE} \\

@@

The data server serves static files from the project's \texttt{clients}
directory at the server URL appended with \texttt{client/filename}.

>>>>

It is suitable to store the data across many storage nodes in what is called a
distributed file system and to to exploit the parallel nature of the records by
breaking up the data sets in pieces and have each piece be processed
separately on a node in a large compute cluster.

% TODO: fixa cites.
Luckily, this is a problem that has already been solved. Google has published
papers on the MapReduce framework \cite{mapreduce}, which allows for parallel
processing of large data sets, and The Google File System \cite{gfs}, a
scalable, distributed file system. The Apache Hadoop \cite{hadoop} project has
published free software implementations of a MapReduce framework and a
distributed file system, both of which build on the ideas in the papers
published by Google.

@@

How to use the Zohmg system is presented in chapter~5, while chapter 6
shows an example work flow.

@@

 yield log.timestamp, dimensions, measurements
\end{verbatim}

@@

The last line \textit{yields} the tuple. This is a Python construct called a
\textit{generator} that lets the map function emit any number of tuples (or
none!) for a single invocation.

@@

In order to import data to Zohmg, the user writes a mapper which Zohmg wraps;
interpreting the output from the mapper program and storing it in HBase.

@@

Based on the query---which the user submits---the corresponding data is
served from HBase as JSONP. The query is a simple definition of wanted row
range, dimensions, and values for these dimensions. The query is submitted
to the data server via HTTP, an example query could look like (the URL is
wrapped to fit the page)

\begin{verbatim}
   http://localhost:8086/data/?t0=20090101
   &t1=20090420&unit=pageviews
   &d0=country&d0v=SE
\end{verbatim}

@@

The data server serves static files from the project's \texttt{clients}
directory at the server URL appended with \texttt{/client/filename}.
